Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-05-20 Master Thesis/synopsis.tex
Use \widetilde instead of \tilde

Let $\mathfrak{X}$ be a model of $K$. For $x\in\mathfrak{X}_1$ the local ring $\mathcal{O}_{\mathfrak{X}, x}$ is a discrete valuation ring and defines a valuation $v_x\in\operatorname{Spv}_\text{d}^{(1)}(K)$. By \cite{Ka86} Theorem 0.8, the map
\[ \mathrm{H}^3(K)\longrightarrow \prod_{x\in\mathfrak{X}_1}\mathrm{H}^3(K_{v_x}) \]
is injective and its image is contained in $\bigoplus \mathrm{H}^3(K_{v_x})$. By \cite{Ka86} Lemma 1.4, for a discrete valuation $v$ of $K$ the map
\[ \mathrm{H}^3(K_v) \longrightarrow \prod_w\mathrm{H}^3(K_w) \]
where $w$ ranges over all rank-$2$ valuations with $v(w) = v$, can be identified with the following map:
\[ {}_\ell\operatorname{Br}(k) \longrightarrow \prod_{\tilde{w}\in\operatorname{Spv}^{(1)}(k)} {}_\ell\operatorname{Br}(k_{\tilde{w}}) \]
where $k = k(v)$. This map is injective by the classical Hasse principle and its image is contained in $\bigoplus {}_\ell\operatorname{Br}(k_{\tilde{w}})$. Combining these maps yields the injection:
\[\Phi: \mathrm{H}^3(K)\longrightarrow \bigoplus_{x\in\mathfrak{X}_1}\  \bigoplus_{\substack{w\in\operatorname{Spv}_\text{rd}^{(2)}(K) \\ v(w) = v_x}} \mathrm{H}^3(K_w) \]
The direct sum ranges over a subset of $|\operatorname{Spv}(K)|$, thus this concludes the proof. 
\end{proof}

@@

First of all, we want to show that $\sigma$ induces an isomorphism between the absolute Galois groups of the constant fields $G_k$ and $G_{k'}$. We need the following Lemma:

>>>>

Let $\mathfrak{X}$ be a model of $K$. For $x\in\mathfrak{X}_1$ the local ring $\mathcal{O}_{\mathfrak{X}, x}$ is a discrete valuation ring and defines a valuation $v_x\in\operatorname{Spv}_\text{d}^{(1)}(K)$. By \cite{Ka86} Theorem 0.8, the map
\[ \mathrm{H}^3(K)\longrightarrow \prod_{x\in\mathfrak{X}_1}\mathrm{H}^3(K_{v_x}) \]
is injective and its image is contained in $\bigoplus \mathrm{H}^3(K_{v_x})$. By \cite{Ka86} Lemma 1.4, for a discrete valuation $v$ of $K$ the map
\[ \mathrm{H}^3(K_v) \longrightarrow \prod_w\mathrm{H}^3(K_w) \]
where $w$ ranges over all rank-$2$ valuations with $v(w) = v$, can be identified with the following map:
\[ {}_\ell\operatorname{Br}(k) \longrightarrow \prod_{\widetilde{w}\in\operatorname{Spv}^{(1)}(k)} {}_\ell\operatorname{Br}(k_{\widetilde{w}}) \]
where $k = k(v)$. This map is injective by the classical Hasse principle and its image is contained in $\bigoplus {}_\ell\operatorname{Br}(k_{\widetilde{w}})$. Combining these maps yields the injection:
\[\Phi: \mathrm{H}^3(K)\longrightarrow \bigoplus_{x\in\mathfrak{X}_1}\  \bigoplus_{\substack{w\in\operatorname{Spv}_\text{rd}^{(2)}(K) \\ v(w) = v_x}} \mathrm{H}^3(K_w) \]
The direct sum ranges over a subset of $|\operatorname{Spv}(K)|$, thus this concludes the proof. 
\end{proof}

@@

We start by showing that $\sigma$ induces an isomorphism between the absolute Galois groups of the constant fields $G_k$ and $G_{k'}$. We need the following Lemma:
